### 2021-09-14 doc/src/MSLevel.tex
Avoid confusion of whether virtual interrupt CSRs are optional

The Advanced Interrupt Architecture assigns other major interrupt
identities in the range 16--63 to additional \emph{local interrupts}
that arise within or in close proximity to the hart, often for
reporting errors.
An optional mechanism is also defined that allows software to
selectively delegate both local and custom interrupts to the next lower
privilege level, or in some cases to inject entirely virtual interrupts
into a lower privilege level.

@@

When supervisor mode is implemented, the Advanced Interrupt
Architecture adds an optional facility for software filtering
of interrupts and for virtual interrupts, making use of new
CSRs \z{mvien}/\z{mvienh} (Machine Virtual Interrupt Enables) and
\z{mvip}/\z{mviph} (Machine Virtual Interrupt-Pending bits).
\emph{Interrupt filtering} permits a local or custom interrupt
to trap to \mbox{M-mode} and then be selectively delegated by
software to supervisor level, even while the corresponding bit in
\z{mideleg}/\z{midelegh} remains zero.
The same hardware may also, under the right circumstances, allow
machine level to assert \emph{virtual interrupts} to supervisor level
that have no connection to any real interrupt events.

>>>>

The Advanced Interrupt Architecture assigns other major interrupt
identities in the range 16--63 to additional \emph{local interrupts}
that arise within or in close proximity to the hart, often for
reporting errors.
A mechanism is also defined that allows software to
selectively delegate both local and custom interrupts to the next lower
privilege level, or in some cases to inject entirely virtual interrupts
into a lower privilege level.

@@

When supervisor mode is implemented, the Advanced Interrupt
Architecture adds a facility for software filtering
of interrupts and for virtual interrupts, making use of new
CSRs \z{mvien}/\z{mvienh} (Machine Virtual Interrupt Enables) and
\z{mvip}/\z{mviph} (Machine Virtual Interrupt-Pending bits).
\emph{Interrupt filtering} permits a local or custom interrupt
to trap to \mbox{M-mode} and then be selectively delegated by
software to supervisor level, even while the corresponding bit in
\z{mideleg}/\z{midelegh} remains zero.
The same hardware may also, under the right circumstances, allow
machine level to assert \emph{virtual interrupts} to supervisor level
that have no connection to any real interrupt events.
